Variational Monte Carlo on bosonic systems

### 2018-03-23 project_1/article/article.tex
Added results that were accidentally removed in a previous commit.

\maketitle

@@

    We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
    sampling. Moreover, we will compute the value for the local energy analytically as well as with a numerical approach.
    In the numerical approach.

@@

>>>>

\maketitle
\tableofcontents

@@

    We will start without importance sampling, that is by employing the simpler and more naïve "brute force" Monte Carlo
    sampling. Moreover, we will compute the value for the local energy analytically as well as with a numerical approach.
    In the numerical approach we employ the well-know approximation for the second derivative,
    \begin{equation}
    		f''(x= \approx \frac{f(x-h) - 2f(x) + f(x+h)}{h^2}.
    \end{equation}

@@

\subsection{Interacting elliptical harmonic oscillator}
         \begin{table}
             \caption{The expected energy, the standard
             deviation, the acceptance ratio and CPU time for each $alpha$
             for the elliptical potential with the interacting wavefunction. We
             have used importance sampling with $\delta t = 0.1$ and $2^{21}$
             Monte Carlo cycles and an additional $10\%$ of that as
             thermalization steps. The hard sphere radius is set to $0.0043$ and
             a $\beta = \lambda = \sqrt{8}$.}
             \centering
             \begin{ruledtabular}
                 \begin{tabular}{ccccc}
                     $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                     &$A$&$t_C$ \\
                     \hline
                     0.2&35.17548&0.05399&0.98995&24.48868\\
                     0.3&27.62004&0.02311&0.98187&13.65132\\
                     0.4&24.97850&0.00827&0.97248&13.54666\\
                     0.5&24.39877&0.00030&0.96140&13.38388\\
                     0.6&24.83863&0.00604&0.94998&13.31570\\
                     0.7&25.82855&0.01059&0.93766&13.20579\\
                     0.8&27.22895&0.01436&0.92375&13.11933\\
                 \end{tabular}
             \end{ruledtabular}
             \label{tab:10_interacting}
         \end{table}

         \begin{table}
             \caption{BLEH}
             \centering
             \begin{ruledtabular}
                 \begin{tabular}{ccccc}
                     $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                     &$A$&$t_C$ \\
                     \hline
                     0.2&181.69371&0.25533&0.98756&199.95366\\
                     0.3&142.61591&0.10782&0.97849&195.80928\\
                     0.4&129.88615&0.04051&0.96862&190.44553\\
                     0.5&127.29926&0.00595&0.95749&195.10368\\
                     0.6&129.97630&0.03300&0.94595&193.22755\\
                     0.7&135.67382&0.05785&0.93330&191.96391\\
                     0.8&143.23238&0.07286&0.92061&192.72399\\
                 \end{tabular}
             \end{ruledtabular}
             \label{tab:50_interacting}
         \end{table}

         \begin{table}
             \caption{BLEH}
             \centering
             \begin{ruledtabular}
                 \begin{tabular}{ccccc}
                     $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                     &$A$&$t_C$ \\
                     \hline
                     0.2&375.04401&0.51475&0.98527&745.21438\\
                     0.3&296.76879&0.20214&0.97534&741.04425\\
                     0.4&270.60830&0.08113&0.94522&723.06823\\
                     0.5&266.37263&0.02020&0.95314&702.71000\\
                     0.6&272.51171&0.07366&0.94112&689.12862\\
                     0.7&285.10285&0.11381&0.92895&707.48248\\
                     0.8&301.40609&0.15458&0.91648&707.86118\\
                 \end{tabular}
             \end{ruledtabular}
             \label{tab:100_interacting}
         \end{table}

         \begin{figure}
             \includegraphics[width=250px]{../data/figures/problem_e.pdf}
             \caption{BLEH}
             \label{fig:interacting}
         \end{figure}
